Production-maintenance scheduling in complex machinery

### 2024-03-20 Paper.tex
Benchmark

 It is easy to create instances that favor each of the models, as having more or less identical machines favors the extended or the compact formulations respectively. For this reason, we have opted for creating three sets of instances, with one of them having several identical machines, one other having many dissimilar machines, and an intermediate set.

 For every instance, we ran the three formulations with a $1$h time limit each. The three formulations are the compact formulation, the extended formulation with exact pricing, and the extended formulation with heuristic pricing.

Each of the results represents the average of the $10$ randomly generated instances according to the relevant specification (all with the same complexity, time periods, number of machines). The Time column will show the average time to optimality, for the instances where optimality is achieved, and the Gap (\%) column will show the average Gap for the instances where it was not. The gap is the relative gap: $\frac{|\text{primal bound} - \text{dual bound}|}{ \min(|\text{primal bound}|, |\text{dual bound}|)}$.

>>>>

 It is easy to create instances that favor each of the models, as having more or less identical machines favors the extended or the compact formulations respectively. For this reason, we have opted for creating three sets of instances, with one of them having several identical machines (one group of $20$), one other having many dissimilar machines ($4$ groups of $2$), and an intermediate set (one group of $5$ and one group of $2$). This means that our test set has $10\cdot 3\cdot 2\cdot 3 = 180$ different tests.

 For every instance, we ran the three formulations with a $30$ minute time limit each. The three formulations are the compact formulation, the extended formulation with exact pricing, and the extended formulation with heuristic pricing.

Each of the results present in Section~\ref{sec:results} represents the average of the $10$ randomly generated instances according to the relevant specification (all with the same complexity, time periods, number of machines). The Time column will show the average time to optimality, for the instances where optimality is achieved, and the Gap (\%) column will show the average Gap for the instances where it was not. The gap is the relative gap: $\frac{|\text{primal bound} - \text{dual bound}|}{ \min(|\text{primal bound}|, |\text{dual bound}|)}$.
